Unshuffling Permutations

### 2016-02-03 new-article.tex
LATIN 2016

\begin{proof}[of Proposition~\ref{proposition:hardness}]
  The problem is certainly in $\NPclass$. We propose a reduction from
  the pattern involvement problem which is known to be
  \NPC~\cite{Bose:Buss:Lubiw:1998}: Given two permutations $\pi$ and
  $\sigma$, decide whether $\sigma$ occurs in $\pi$ (as an
  order-isomorphic pattern).

>>>>

\begin{proof}[of Proposition~\ref{proposition:hardness}]
  The problem is certainly in $\NPclass$. We propose a reduction from
  the pattern involvement problem which is known to be
  \NPC~\cite{Bose:Buss:Lubiw:1998}. Given two permutations $\pi$ and
  $\sigma$, pattern involvement problem is to decide whether $\sigma$ occurs in
  $\pi$ (as an order-isomorphic pattern).
